%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}
\rfoot{{\color{HF_color} \thepage \ of \ 1, Updated \today}}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large +90(542)-591-5978 \\
            \large \href{mailto:umitozdemirf@gmail.com}{umitozdemirf@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Ümit Özdemir} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{QA Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/umttozdmr/}{Linkedin} } \\
            \href{https://github.com/umttozdmr}{Github}
    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.2cm}
\begin{center}
    {\color{UI_blue} \Large{COVER LETTER}}
\end{center}


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}
Dear Hiring Manager, % OR To whom this may concern, 

As a highly skilled QA Engineer with over 4 years of experience, I am excited to express my interest in the QA Engineer position at your company. I am confident that my experience and skill set align well with your requirements, and I am eager to make a valuable contribution to your team.

During my tenure as a QA Automation Consultant in a consulting firm, I have gained a wealth of experience managing various projects and teams. In fact, I have been involved in more than 10 projects/customers, which has honed my ability to manage multiple priorities and deadlines with ease. Throughout these projects, I have utilized my advanced knowledge of Python, PyTest, Behave (UI & Service & Mobile), Java, Selenium (UI), Ruby, Capybara, RSpec, Appium (UI & Service & Mobile) to build various infrastructures and provide consulting services to customers.

In all my projects, I developed them in accordance with software development standards such as SOLID Principles, OOP, and the PageObject model. I am proud to have also developed an automation infrastructure using Go and the godog library to improve my skills, as well as a k6io performance test project integrated into pipelines to enable effective performance testing. Additionally, I have taken an active role in teams using performance testing tools such as JMeter, Locust, Gatling and developed test scenarios.

I understand the importance of reporting in testing, and I have established a logging and reporting mechanism in all my projects to obtain effective reports. I have also prepared pipelines for all projects and obtained an ISTQB certificate to develop test principles and basic test techniques. My passion for DevOps has led me to do PoCs on containerization and networking, and I have gained valuable experience in tools such as Docker and Kubernetes. I am proud to have received the CKA (Certified Kubernetes Administrator) Certificate, which I believe is instrumental in improving CI/CD processes on the QA side.

In conclusion, my educational foundation and passion for furthering projects that build loyalty and, in turn, grow revenue make me an excellent candidate for this position. Please find my attached application for additional details regarding my expertise and achievements. I would welcome the opportunity to meet with you and discuss how I can make a valuable contribution to your ongoing growth and continued success.

Thank you for considering my application. \par

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Sincerely \\ Ümit Özdemir 

\end{document}
